Aligning marine species range data to better serve science and conservation

### 2016-05-17 data_explore/data_explore_am_thresh.Rmd
updating manuscript to ecology letters standards

ggsave(file.path(dir_fig, 'si_am_threshold.tif'), device = 'tiff', 
       width = 11.4, height = 6, units = 'cm')
ggsave(file.path(dir_fig, 'si_am_threshold.png'), 
       width = 11.4, height = 6, units = 'cm')

@@

ggsave(file.path(dir_fig, 'si_am_threshold2.tif'), device = 'tiff', 
       width = 17.8, height = 9, units = 'cm')
ggsave(file.path(dir_fig, 'si_am_threshold2.png'), 
       width = 17.8, height = 9, units = 'cm')

@@

ggsave(file.path(dir_fig, 'si_ribbon_am_threshold.tif'), device = 'tiff', 
       width = 11.4, height = 6, units = 'cm')
ggsave(file.path(dir_fig, 'si_ribbon_am_threshold.png'), 
       width = 11.4, height = 6, units = 'cm')

>>>>

ggsave(file.path(dir_fig, 'si_am_threshold.tif'), device = 'tiff', 
       width = 11.4, height = 6, units = 'cm', dpi = 600)
ggsave(file.path(dir_fig, 'si_am_threshold.png'), 
       width = 11.4, height = 6, units = 'cm', dpi = 600)

@@

ggsave(file.path(dir_fig, 'si_am_threshold2.tif'), device = 'tiff', 
       width = 17.8, height = 9, units = 'cm', dpi = 600)
ggsave(file.path(dir_fig, 'si_am_threshold2.png'), 
       width = 17.8, height = 9, units = 'cm', dpi = 600)

@@

ggsave(file.path(dir_fig, 'si_ribbon_am_threshold.tif'), device = 'tiff', 
       width = 11.4, height = 6, units = 'cm', dpi = 600)
ggsave(file.path(dir_fig, 'si_ribbon_am_threshold.png'), 
       width = 11.4, height = 6, units = 'cm', dpi = 600)

### 2016-05-17 manuscript-main-v2.Rmd
updating manuscript to ecology letters standards

---
title: "Aligning marine species range data to better serve science and conservation"
author: Casey O'Hara^1^, Jamie C. Afflerbach^1^, Courtney Scarborough^1^, Benjamin
  S. Halpern^1,2,3^
output:
  html_document:
    highlight: haddock
    number_sections: no
    theme: spacelab
    toc: no
  pdf_document:
    number_sections: no
    toc: no
  word_document: default
bibliography: refs/zotero_lib.bib
csl: refs/ecology-letters.csl
---

@@

``` {r abstract, child = 'ms_1_abst_sig.Rmd'}
```

>>>>

---
title: "Aligning marine species range data to better serve science and conservation"
author: Casey O'Hara^1^, Jamie C. Afflerbach^1^, Courtney Scarborough^1^, Benjamin
  S. Halpern^1,2,3^
csl: refs/ecology-letters.csl
output:
  word_document: default
  pdf_document:
    number_sections: no
    toc: no
  html_document:
    highlight: haddock
    number_sections: no
    theme: spacelab
    toc: no
bibliography: refs/zotero_lib.bib
---

@@

``` {r abstract, child = 'ms_1_abst_150wd.Rmd'}
```

### 2016-05-17 manuscript-main.Rmd
updating manuscript to ecology letters standards

---
title: "Aligning marine species range data to better serve science and conservation"
author: Casey O'Hara^1^, Jamie C. Afflerbach^1^, Courtney Scarborough^1^, Benjamin
  S. Halpern^1,2,3^
output:
  word_document: default
  pdf_document:
    number_sections: no
    toc: no
  html_document:
    highlight: haddock
    number_sections: no
    theme: spacelab
    toc: no
---

>>>>

---
title: "Aligning marine species range data to better serve science and conservation"
author: Casey O'Hara^1^, Jamie C. Afflerbach^1^, Courtney Scarborough^1^, Benjamin
  S. Halpern^1,2,3^
csl: refs/ecology-letters.csl
output:
  word_document: default
  pdf_document:
    number_sections: no
    toc: no
  html_document:
    highlight: haddock
    number_sections: no
    theme: spacelab
    toc: no
bibliography: refs/zotero_lib.bib
---
